This project aims to present solutions (queries) on a dataset that contains information about taxi rides in New York City. Using Siddhi, which allows creating Apps where we can write Streaming processing and Complex Event Processing rules with Siddhi Streaming SQL, and WSO2 Streaming Processor which allows to integrate Siddhi Apps, we intend to present solutions for the following questions: 

\begin{itemize}
\item \textbf{Q1:} Find the top 10 most frequent routes during the last 30 minutes. 
\item \textbf{Q2:} Identify areas that are currently most profitable for taxi drivers.
\item \textbf{Q3:} Alert whenever the average idle time of taxis is greater than a given amount of time (say 10 minutes).
\item \textbf{Q4:} Detect congested areas.
\item \textbf{Q5:} Select the most pleasant taxi drivers. 
\end{itemize}

To divide the map into an NxN grid, given the longitude and latitude values of the event, we use the following formulas to calculate the grid cell:
\begin{align}
LONG_-CELL = round((longitude - MIN_-LON) / LON_-DELTA) \\
LAT_-CELL = round((MAX_-LAT - latitude) / LAT_-DELTA)
\end{align}

where $MIN_-LON = -74.916578$, $MAX_-LAT = 41.47718278$ and $LON_-DELTA$ and $LAT_-DELTA$ are deltas corresponding to the intended N for the NxN grid. \par
This report is structured as follows: in section 2 we present the rationale for solving each issue as well as our interpretation of the issue; in section 3, we present in greater detail our solution to one of the questions, as well as the results obtained; and, finally, in section 4, we present our conclusions about the solutions and results obtained. 